### 2022-06-27 README.Rmd
updated broken URL and removed travis build link

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![Build Status](https://app.travis-ci.com/SabaLab/diffEnrich.svg?branch=master)](https://app.travis-ci.com/SabaLab/diffEnrich)

@@

When there are two or more gene lists to compare and the background gene list is not clearly defined, as is often the case in protein modification experiments, we propose a differential enrichment analysis. In this analysis, we compare the proportion of genes/proteins from one gene list associated with a particular pathway to the proportion of genes/proteins from a second gene list that are associated with that pathway. To easily execute this analysis, we have designed an R package that uses the KEGG REST API to obtain the most recent version of the KEGG PATHWAY ( [Kanehisa and Goto, 2000](https://www.ncbi.nlm.nih.gov/pubmed/10592173)) database to initially identify functional enrichment within a gene list using the entire KEGG transcriptome as the background data set and then to identify differentially enriched pathways between two gene lists. This R package includes a function to generate a "differential enrichment" graphic.

>>>>

<!-- README.md is generated from README.Rmd. Please edit that file -->

@@

When there are two or more gene lists to compare and the background gene list is not clearly defined, as is often the case in protein modification experiments, we propose a differential enrichment analysis. In this analysis, we compare the proportion of genes/proteins from one gene list associated with a particular pathway to the proportion of genes/proteins from a second gene list that are associated with that pathway. To easily execute this analysis, we have designed an R package that uses the KEGG REST API to obtain the most recent version of the KEGG PATHWAY ( [Kanehisa and Goto, 2000](https://pubmed.ncbi.nlm.nih.gov/10592173/)) database to initially identify functional enrichment within a gene list using the entire KEGG transcriptome as the background data set and then to identify differentially enriched pathways between two gene lists. This R package includes a function to generate a "differential enrichment" graphic.
